Waggle dance distributions quantify collective foraging in honey bee colonies: Supplementary material

### 2022-04-05 analysis/manuscript/supplementary_material.Rmd
ran code and updated results of fitting
reran to make plots with out histograms for easier viewing in the SM

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(size = 18)
    )
)

library(dplyr)
library(kableExtra)
library(flextable)
library(tibble)
```

@@

@@

# load fit data
df <- readRDS(file = "../results/site_fit_results.Rda")

>>>>

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
library(cowplot)
theme_set(
  theme_classic() +
    theme(
      text = element_text(size = 18)
    )
)

library(dplyr)
library(kableExtra)
library(flextable)
library(tibble)
library(purrr)

# load fitting results / stats
load("results/site_fit_results.Rdata")
```

@@

```{r, all-model-fits}

plots <- map(all_sites, 2)
plots <- plots %>%
  map(
    ~ {.x + theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank()
    )}
  )
print(plots$BEL)

plot_grid(plotlist = plots, nrow = 5)

```

@@

# load fit data
load("results/site_fit_results.Rdata")

# group all site results together
df <- map(all_sites, 1) %>%
  bind_rows()
